\cvsection{Projects}



\cvevent{Learning Lantern}{Graduation Project -- Excellent -- \faGithub{\href{https://github.com/learning-lantern}{Source Code}}}{Jan. 2022 -- Jun. 2022}{Asyut, Egypt}
\begin{itemize}
    \item A complete Learning Management System that allows institutes and universities to get their learning portal easily, with integrated and easy-to-use cloud services and content-creating tools for leveraging the online education processes.
    % \item Led the project team and the back-end team. Kept encouraging my teammates in all phases to do as best as they could.
    % \item Applied software engineering practices learned how to distribute the tasks for the team, and made weekly sprint plans. Met our academic teachers in the first phase and gathered our requirements.
    \item Took ownership to design the database and normalized it to be as optimized as possible.
    \item Built the Authentication and Authorization service using ASP.NET Core Identity, JWT Bearer, and Email Sender service.
    % \item Injected Swagger service to test and document my API and implemented its security definition for authentication.
    \item Designed the app first in the monolithic architecture and then upgraded it to the microservices architecture.
    \item Developed Ocelot API Gateway and rebuilt Authentication service using MediatR pattern. Structured development plans for services.
    \item Accomplished To Do, Text Lessons using ASP.NET Core Web API and Video services using ASP.NET Core SignalR and WebRTC.
    % \item Tested services and APIs using Postman and Unit Testing.
    \item Deployed the database on Azure SQL Database and the application on Azure App Service.
    \item Used Azure DevOps for the deployment of our Docker containers. Stored files and videos on Azure Blob Storage.
\end{itemize}

\divider

\cvevent{Fathy.Common}{Open-Source -- \faGithub{\href{https://github.com/SWE-Ahmed-Osman/Fathy.Common}{Source Code}}}{Oct. 2022 -- Present}{Asyut, Egypt}
\begin{itemize}
    \item An open-source project I made to facilitate developing the most common .NET services for developers and let them be free to customize it, with the best practices.
    \item Implemented Swagger definitions, Email sender, Authentication and JWT services, and Azure Blob Storage service.
\end{itemize}

\divider

\cvevent{Ahl AlQuran Academy}{Distributed Database Course -- \faGithub{\href{https://github.com/ahl-alquran-academy}{Source Code}}}{Sep. 2021 -- Jan. 2022}{Asyut, Egypt}
\begin{itemize}
    \item A platform for memorizing and reviewing the Noble Quran and learning the provisions of intonation and readings.
    \item Designed the database, after that mapped the relations, then normalized and implemented them on MySQL Server.
\end{itemize}

\cvevent{Runner Wheel 3D}{Computer Animation Course -- \faGithub{\href{https://github.com/SWE-Ahmed-Osman/Runner-Wheel-3D/releases/tag/v0.1.0}{Source Code}}}{Dec. 2021 -- Jan. 2022}{Asyut, Egypt}
\begin{itemize}
    \item An endless runner game for Android and Windows.
    \item Designed the game on Unity Engine and developed by C\#.
\end{itemize}