%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.7, 9 August 2023) written by LianTze Lim (liantze@gmail.com). Compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and packages.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1cm,right=1cm,top=1cm,bottom=1cm,columnsep=1cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
% WHEN COMPILING WITH XELATEX PLEASE USE
% xelatex -shell-escape -output-driver="xdvipdfmx -z 0" sample.tex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Times New Roman}
  \setsansfont{Arial}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Use ArabTex package for Arabic language.
\usepackage{arabtex}
\usepackage{utf8}

\begin{document}

\setcode{utf8}

\name{Ahmed Mohamed Fathy Osman}
\tagline{Software Engineer}
%% You can add multiple photos on the left or right
% \photoR{2.8cm}{Globe_High}
% \photoL{2.5cm}{Yacht_High,Suitcase_High}

\personalinfo{%
  % Not all of these are required!
  \email{SWE.Ahmed.Osman@gmail.com}
  \phone{+20 120 873 1604}
  % \mailaddress{Åddrésş, Street, 00000 Cóuntry}
  \location{Cairo, Egypt}
  % \homepage{www.homepage.com}
  % \twitter{@twitterhandle}
  \linkedin{SWE-Ahmed-Osman}
  \github{SWE-Ahmed-Osman}
  % \orcid{0000-0000-0000-0000}
  %% You can add your arbitrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]

  %% Or you can declare your field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
  %%
  %% For services and platforms like Mastodon where there isn't a
  %% straightforward relation between the user ID/nickname and the hyperlink,
  %% you can use \printinfo directly e.g.
  % \printinfo{\faMastodon}{@username@instace}[https://instance.url/@username]
  %% But if you want to create new dedicated info fields for
  %% such platforms, then use \NewInfoField* with a star:
  % \NewInfoField*{mastodon}{\faMastodon}
  %% then you can use \mastodon, with TWO arguments where the 2nd argument is
  %% the full hyperlink.
  % \mastodon{@username@instance}{https://instance.url/@username}
}

\makecvheader

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Education}

\cvevent{B.Sc. Degree in Bachelor Degree of Computers and Information Majoring in Computer Science}{Assiut University}{Sep. 2018 -- Jul. 2022}{Assiut, Egypt}

\cvsection{Experience}

\cvevent{Software Engineer}{Freelance}{Jul. 2022 -- Present}{Assiut, Egypt}
\begin{itemize}
    \item I work as a Freelancer during and after Military service to improve my skills and raise my experience.
    \item I integrate my educational knowledge with industry experience to start my journey in the software industry.
\end{itemize}

\cvsection{Projects}

\cvevent{\href{https://github.com/learning-lantern}{Learning Lantern}}{Graduation Project -- Excellent}{Jan. 2022 -- Jul. 2022}{}
\begin{itemize}
    \item A complete Learning Management System that allows institutes and universities to get their learning portal easily, with integrated and easy-to-use cloud services and content-creating tools for leveraging the online education processes.
    \item Contributed with my team to design the database, then normalized it to be as optimized as possible.
    \item Built the Authentication and Authorization service using ASP.NET Core Identity, JWT Bearer, and Email Sender service.
    \item Injected Swagger service to test and document my API and implemented its security definition for authentication.
    \item Designed the app first in the monolithic architecture, and after that upgraded it to the microservices architecture.
    \item Developed Ocelot API Gateway and rebuilt Authentication service using MediatR pattern. Structured development plans for services.
    \item Accomplished To Do, Text Lessons using ASP.NET Core Web API and Video services using ASP.NET Core SignalR and WebRTC.
    \item Tested the services and the APIs using Postman and Unit Testing.
    \item Deployed the database on Azure SQL Database and the application on Azure App Service.
    \item Used Azure DevOps for the deployment of our Docker containers. Stored files and videos on Azure Blob Storage.
\end{itemize}

\divider

\cvevent{\href{https://github.com/SWE-Ahmed-Osman/mustafakamel.NET}{Mustafa Kamel Portfolio}}{Freelance}{Sep. 2022 -- Oct. 2022}{}
\begin{itemize}
    \item Learned more about environment variables and dependency injection and used it professionally.
    \item Injected the swagger service implemented its security definition for authentication and used it to test and document my API.
    \item Approached code first and used Entity Framework Core (ORM) for database migrations with SQL Server and hosted my database on Azure SQL Database.
    \item Used LINQ for querying and data manipulation and accomplished complex mapping using Automapper.
    \item Applied ASP.NET Core Identity with JSON Web Token for authentication and authorization.
    \item Interacted with files and videos and stored them on Azure Blob Storage service and deployed the application on Azure App Service.
\end{itemize}

\divider

\cvevent{\href{https://github.com/SWE-Ahmed-Osman/Fathy.Common}{Fathy.Common}}{Open-Source}{Oct. 2022 -- Present}{}
\begin{itemize}
    \item An open-source project I made to facilitate developing the most common .NET services for developers and let them be free to customize it, with the best practices.
    \item Implemented Swagger definitions, Email sender, Authentication and JWT services, and Azure Blob Storage service.
\end{itemize}

\divider

\cvevent{\href{https://github.com/ahl-alquran-academy}{Ahl AlQuran Academy}}{Distributed Database Course}{Sep. 2021 -- Jan. 2022}{}
\begin{itemize}
    \item A platform for memorizing and reviewing the Noble Quran and learning the provisions of intonation and readings.
    \item Designed the database, after that mapped the relations, then normalized and implemented them on MySQL Server.
\end{itemize}

\cvevent{\href{https://github.com/SWE-Ahmed-Osman/Runner-Wheel-3D/releases/tag/v0.1.0}{Runner Wheel 3D}}{Computer Animation Course}{Dec. 2021 -- Jan. 2022}{}
\begin{itemize}
    \item An endless runner game for Android and Windows.
    \item Designed the game on Unity Engine and developed it by C\#.
\end{itemize}

\cvsection{Volunteer Experience}

\cvevent{Mentor \& Contestant}{ICPC Assiut University Community}{Oct. 2018 -- Jun. 2022}{Assiut, Egypt}
The main goal of this community is to improve programming, problem-solving, and algorithmic skills of all students in Egypt.

\divider

\cvevent{Ambassador}{Information Technology Institute (ITI)}{Mar. 2021 -- Oct. 2021}{Assiut, Egypt}
A leading national institute in ICT human capacity-building. Established with the Egyptian MCIT.

\divider

\cvevent{Linux \& Embedded Systems Instructor}{Tec Youth}{Nov. 2020 -- Jun. 2022}{Assiut, Egypt}
Preparing youth cadres who are aware of technological development and keep abreast of the labor market. Youth Supporting Youth.

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

% \cvsection{Philosophy}

% \begin{quote}
    % \begin{RLtext}
        % `إِنَّ اللَّهَ لَا يُغَيِّرُ مَا بِقَوْمٍ حَتَّىٰ يُغَيِّرُوا مَا بِأَنفُسِهِمْ'
    % \end{RLtext}
% \end{quote}

\cvsection{Summary}

\begin{itemize}
    \item With over 1 year of experience in Back-End Development and industry experience in building websites and web applications.
    \item Specialist in .NET Core Frameworks. Satisfactory background working with Angular, React, and Vue.js on multiple projects.
    \item Have powerful computer science knowledge and I am eager to learn more concepts and dive deep into computer science tracks.
    \item Good in Object-Oriented Programming, Data Structures, Algorithms, Database Systems, Design Patterns, and Problem-Solving.
    \item Practiced competitive programming a lot in college and enjoyed competing with my colleagues and mentors and participating in many programming competitions.
    \item Passionate about learning .NET, Back-End technologies, DevOps, Web 3, Blockchain, Linux, Virtualization, and Cloud Computing.
    \item Detailed-Oriented, responsible, committed engineer, with a get-it-done, on-time, and high-quality product spirit. Self-quick learner, self-motivated, and social.
\end{itemize}

\cvsection{Skills}

\cvtag{C / C++}
\cvtag{Java}
\cvtag{C\#}
\cvtag{Python}
\cvtag{Bash}\\
\cvtag{SQL}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{JavaScript}\\

\divider

\cvtag{Object-Oriented Programming (OOP)}\\
\cvtag{Data Structures}
\cvtag{Algorithms}\\
\cvtag{Design Patterns}
\cvtag{Problem Solving}\\
\cvtag{Database Systems}
\cvtag{Computer Networking}\\
\cvtag{Software Engineering Practices}\\

\divider

\cvtag{.NET Framework}\\
\cvtag{ASP.NET Core MVC}\\
\cvtag{ASP.NET Core Web API}\\
\cvtag{ASP.NET Core SignalR}\\
\cvtag{ASP.NET Core Identity}\\
\cvtag{ASP.NET Core Razor Pages}\\
\cvtag{Entity Framework Core}\\
\cvtag{Microsoft SQL Server}\\
\cvtag{Language Integrated Query (LINQ)}\\

\divider

\cvtag{Heroku}
\cvtag{Microsoft Azure}\\
\cvtag{Docker}
\cvtag{Cloud Computing}\\
\cvtag{Azure SQL Database}\\

\divider

\cvtag{REST APIs}\\
\cvtag{WebRTC}
\cvtag{WebSocket}\\
\cvtag{Unit Testing}
\cvtag{Microservices}\\
\cvtag{JSON Web Token (JWT)}\\
\cvtag{Clean Code}
\cvtag{Git}
\cvtag{Unix / Linux}\\

\divider

\cvtag{Presentation Skills}
\cvtag{Interpersonal Skills}\\
\cvtag{Communication Skills}
\cvtag{Teamwork}\\

\cvsection{Certifications}

\cvachievement{\faCode}{\href{https://icpc.global/ICPCID/0B2QPKFH8JMG}{4th Place in The 2019 Assuit Collegiate Programming Contest}}{}

\cvachievement{\faCode}{\href{https://icpc.global/ICPCID/0B2QPKFH8JMG}{23th Place in The 2020 Upper Egypt Collegiate Collegiate Programming Contest}}{}

\cvachievement{\faDatabase}{\href{https://drive.google.com/file/d/1Gmcf33B4_rAJ-FqTkQXJ2-6kYhJiofP3/view?usp=sharing}{Database Fundamentals}}{}

\cvachievement{\faNetworkWired}{\href{https://drive.google.com/file/d/1hkGmHOcu0o5RtP1xld4zJANnbUo3VLAn/view?usp=sharing}{Computer Network Fundamentals}}{}

\cvachievement{\faDatabase}{\href{https://www.linkedin.com/learning/certificates/8f567423b37c6ceebbe4263ed47f4b4f667d8740205d0136c3e0c97a0eb52e0c?trk=share_certificate}{Programming Foundations: Databases}}{}

\cvachievement{\faNetworkWired}{\href{https://www.linkedin.com/learning/certificates/98e65da2aab413107ec6b20b7b5b18d6451ede41ae1d3ad4f0cdb8aadf9d055c?trk=share_certificate}{CompTIA Network+ (N10-007)}}{}

\cvachievement{\faCode}{\href{https://www.linkedin.com/learning/certificates/b99dfd8b91f10b7994e8bba707ad44d0edd27ddd7a6ddeeba5bef3d5dd9acebb?trk=share_certificate}{Succeeding in Web Development: Full Stack and Front End}}{}

\cvachievement{\faGlobe}{\href{https://www.coursera.org/account/accomplishments/certificate/TLFB2AJCZ2TT}{Technical Support Fundamentals}}{}

\cvachievement{\faNetworkWired}{\href{https://www.coursera.org/account/accomplishments/certificate/7Q3BAYSZ4U4F}{The Bits and Bytes of Computer Networking}}{}

\cvachievement{\faLinux}{\href{https://www.coursera.org/account/accomplishments/certificate/K7HUWLJX6Q2D}{Operating Systems: Becoming a Power User}}{}

\cvachievement{\faGlobe}{\href{https://www.coursera.org/account/accomplishments/certificate/ASHRTZNTJHRV}{System Administration and IT Infrastructure Services}}{}

\cvachievement{\faCloud}{\href{https://www.coursera.org/account/accomplishments/certificate/7LCUGZHAPXEW}{Cloud Computing Basics (Cloud 101)}}{}

\cvachievement{\faTrophy}{\href{https://www.coursera.org/account/accomplishments/certificate/2HUDKX5FU5MH}{English for Career Development}}{}

\cvachievement{\faGrinBeam}{\href{https://www.coursera.org/account/accomplishments/certificate/SPSF7BJ6LW76}{Speak English Professionally: In Person, Online \& On the Phone}}{}

\cvsection{Languages}

\cvskill{Arabic}{4}

\divider

\cvskill{English}{3}

% \cvsection{Referees}

% \cvref{name}{email}{mailing address}
% Available upon request.

\end{paracol}

\end{document}