


\cvsection{Experience}



\cvevent{Back-End Engineer}{Axapta. Ltd}{Dec. 2023 -- Present}{Remote}
{\bfseries Kaizen}
\begin{itemize}
    \item Programmed REST APIs with C\# 12 and .NET 8. Organized sprints and tasks on Jira and applied Agile engineering practices.
    \item Created Azure Storage account and initiated containers.
    \item Increased API security by using Shared Access Signature (SAS) to make an expiration duration for Blobs and Containers.
    \item Tested services and APIs using Postman and Swagger.
\end{itemize}

\divider

\cvevent{Software Engineer}{Freelance}{Jul. 2022 -- Present}{Remote}
\begin{itemize}
    \item Worked as a Freelancer during and after Military Service to improve my skills and raise my experience.
    \item Integrated my educational knowledge with industry experience to start my journey in the software industry.
\end{itemize}

{\bfseries Mustafa Kamel Portfolio}\hspace{0.5cm}{\faGithub{\href{https://github.com/SWE-Ahmed-Osman/mustafakamel.NET}{Source Code}}}\hspace{0.5cm}{\small Sep. 2022 -- Oct. 2022}
\begin{itemize}
    \item Learned more about environment variables and dependency injection and used it professionally.
    \item Injected the swagger service implemented its security definition for authentication and used it to test and document my API.
    \item Approached code first and used Entity Framework Core (ORM) for database migrations with SQL Server and hosted my database on Azure SQL Database.
    \item Used LINQ for querying and data manipulation and accomplished complex mapping using Automapper.
    \item Applied ASP.NET Core Identity with JSON Web Token for authentication and authorization.
    \item Interacted with files and videos and stored them on Azure Blob Storage service and deployed the application on Azure App Service.
\end{itemize}